Functional Analyses of Distinct Oxygen Concentrations and Light Niches of *Prochlorococcus marinus*

### 2024-02-06 Code/Manuscript_O2.Rmd
Added more GAM figs

PurParPlot_cap <- glue("**The absorbed Photosynthetically Usable Radiation (PUR) (µmol photons m^-2^ s^-1^) vs. the Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^).**",
                       "The correlation between PAR, plotted on the x-axis and absorbed PUR, plotted on the y-axis, are colored for each spectral waveband; blue for 450 nm, red for 660 nm and black for white LED full spectrum light.",
                       "The grey dashed line represents a hypothetical one to one correlation.",
                       "**A.** is *Prochlorococcus marinus*  MED4.",
                       "**B.** is *Prochlorococcus marinus*  SS120.",
                       "**C.** is *Prochlorococcus marinus*  MIT9313.",

@@

ProchloroElectronTrans_cap <- glue("**Occurance of electron transport complexes data from the Ocean Protein Portal. X-axis indicates the depth (m) of occurance and the y-axis is the oxygen concentration (µM) **",
                       "Rows are...",
                       "Columns are...",

@@

%%%% Insert GAM figures  %%%

@@

MED4GAM_cap <- glue("** The Generalized Additive Models (GAM) for red light at 660 nm and blue light at 450 nm.  The x-axis is photoperiod (h) and the y-axis is the Photosynethetic Active Radiation (PAR) (µmole photons m-2 s-1) **",
                       "Rows are...",
                       "Columns are...",

@@

@@

%%%% Insert OceanFtsHRibosomeProteins figure from OceanPortal repository  %%%

@@

ProchloroMetabDepthO2_cap <- glue("**Protein turnover complexes data from the Ocean Protein Portal. X-axis indicates the depth (m) of occurance and the y-axis is the oxygen concentration (µM) **",
                       "Rows are...",
                       "Columns are...",

>>>>

PurParPlot_cap <- glue("**The absorbed Photosynthetically Usable Radiation (PUR) (µmol photons m^-2^ s^-1^) vs. the Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^).**",
                       "The correlation between PAR, plotted on the x-axis and absorbed PUR, plotted on the y-axis, are colored for each growth spectral waveband; blue for 450 nm, red for 660 nm and black for white LED full spectrum light.",
                       "The grey dashed line represents a hypothetical one to one correlation.",
                       "**A.** is *Prochlorococcus marinus*  MED4.",
                       "**B.** is *Prochlorococcus marinus*  SS120.",
                       "**C.** is *Prochlorococcus marinus*  MIT9313.",

@@

ProchloroElectronTrans_cap <- glue("**Occurance of electron transport complexes data from the Ocean Protein Portal. X-axis is the oxygen concentration (µM) and the y-axis indicates the depth (m) of occurance**",
                       "Rows are...",
                       "Columns are...",

@@

%%%% Insert GAM figures to show lab results confirming Ocean Protein Portal environment results %%%

@@

MED4GAM_cap <- glue("** The Generalized Additive Models (GAM) for red light at 660 nm and blue light at 450 nm.  The x-axis is photoperiod (h) and the y-axis is the Photosynethetic Active Radiation (PAR) (µmol photons m^-2^ s^-1^) **",
                       "Rows are...",
                       "Columns are...",

@@

```{r SS120GAM,  fig.cap = SS120GAM_cap, fig.height = 10, fig.width = 10, echo = FALSE}

SS120GAM_cap <- glue("** The Generalized Additive Models (GAM) for red light at 660 nm and blue light at 450 nm.  The x-axis is photoperiod (h) and the y-axis is the Photosynethetic Active Radiation (PAR) (µmol photons m^-2^ s^-1^) **",
                       "Rows are...",
                       "Columns are...",

knitr::include_graphics(file.path(FiguresIn, "PICO_Hypervolume_GAM_SS120_Oxy_.png"))

```{r MIT9313GAM,  fig.cap = MIT9313GAM_cap, fig.height = 10, fig.width = 10, echo = FALSE}

MIT9313GAM_cap <- glue("** The Generalized Additive Models (GAM) for red light at 660 nm and blue light at 450 nm.  The x-axis is photoperiod (h) and the y-axis is the Photosynethetic Active Radiation (PAR) (µmol photons m^-2^ s^-1^) **",
                       "Rows are...",
                       "Columns are...",

knitr::include_graphics(file.path(FiguresIn, "PICO_Hypervolume_GAM_MIT9313_Oxy_.png"))

@@

%%%% OceanFtsHRibosomeProteins figure from OceanPortal repository  %%%

@@

ProchloroMetabDepthO2_cap <- glue("**Protein turnover complexes data from the Ocean Protein Portal. The x-axis is the oxygen concentration (µM) and the y-axis indicates the depth (m) of occurance**",
                       "Rows are...",
                       "Columns are...",
